### 2016-08-18 ms/ms.tex
added story board
worked on discussion

Flower-visitors to plants in hedgerows and unrestored controls were
netted for one hour of active search time (the timer was paused when
handling specimens). Honeybees (\textit{Apis mellifera}) were not
collected because their abundance is determined largely by the
placement of hives throughout the region by bee-keepers. All other
insect flower visitors that touched the reproductive parts of the
flower were collected; however, here we focus only on wild bees and
syrphids (representing 49 and 19 percent of records, respectively),
the most abundant and effective pollinators in the system (C. Kremen,
A. Klein and L. Morandin, unpublished data). Bee and syrphid specimens
were identified to species (or morpho-species for some bee specimens
in the genera \textit{Nomada} and \textit{Sphecodes}) by expert
taxonomists.

@@

The majority ($76\%$) of the sites tests underwent at least one
significant reorganization of interactions (Fig.~
\ref{fig:changePoints}). There were no consistent trends as to when
change points occurred within assembling hedgerows or across all sites,
except many site had changing points between year 2009 and 2011 (Fig.~
\ref{fig:changePoints}). In California, 2011 marked the beginning of a
multi year drought. In the assembling hedgerows were not sampled in
2010, so disentangling whether the changing points are due to skipping
a year of assembly or the drought is not impossible.

All five of the assembling hedgerows experienced changing points,
whereas only $40\%$ and $81\%$ of non-assembling hedgerows and field
margins, respectively, underwent significant interaction
reorganizations. Assembling hedgerows experienced significantly more
changing points than the non-assembling networks (difference in the
odds ratios between assembling and non-assembling networks, $3.316$,
$95\%$ CI $[1.314, 8.572]$, $p$-value= $0.0117$). Network assembly
following restoration is thus punctuated by more interaction
reorganizations than would be expected by environmental shifts that
would effect assembling and non-assembling networks equally.

@@

@@

We would like to thank Leto Peel and Aaron Clauset for their
invaluable discussions and for help with the change point analysis.
We thank the growers and land owners that allowed us to work on their
property.  We also greatly appreciate the identification assistance of
expert taxonomists Martin Hauser, Robbin Thorp and Jason Gibbs.  This
work was supported by funding from the Army Research Office
(W911NF-11-1-0361 to CK), the Natural Resources Conservation Service
(CIG-69-3A75-12-253, CIG-69-3A75-9-142, CIG-68-9104-6-101 and
WLF-69-7482-6-277 to The Xerces Society), the National Science
Foundation (DEB-0919128 to CK), The U.S.  Department of Agriculture
(USDA-NIFA 2012-51181-20105 to Michigan State University).  Funding
for LCP was provided by an NSF Graduate Research Fellowship and the
USDA NIFA Graduate Fellowship. FUNDING FOR MARILLIA.

>>>>

Flower-visitors to plants in hedgerows and unrestored controls were
netted for one hour of active search time (the timer was paused when
handling specimens). Honeybees (\textit{Apis mellifera}) were not
collected because their abundance is determined largely by the
placement of hives throughout the region by bee-keepers. All other
insect flower visitors that touched the reproductive parts of the
flower were collected; however, here we focus only on wild bees and
syrphids (representing 49 and 19 percent of records, respectively),
the most abundant and effective pollinators in the system (C. Kremen,
A.~ Klein and L.~ Morandin, unpublished data). Bee and syrphid specimens
were identified to species (or morpho-species for some bee specimens
in the genera \textit{Nomada} and \textit{Sphecodes}) by expert
taxonomists.

@@

The majority ($76\%$) of the sites tests underwent at least one
significant reorganization of interactions (Fig.~
\ref{fig:changePoints}).  All five of the assembling hedgerows
experienced changing points, whereas only $40\%$ and $81\%$ of
non-assembling hedgerows and field margins, respectively, underwent
significant interaction reorganizations. Assembling hedgerows
experienced significantly more changing points than the non-assembling
networks (difference in the odds ratios between assembling and
non-assembling networks, $3.316$, $95\%$ CI $[1.314, 8.572]$,
$p$-value= $0.0117$). Network assembly following restoration is thus
punctuated by more interaction reorganizations than would be expected
by environmental shifts that would effect assembling and
non-assembling networks equally.

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where patterns of
interactions undergo several significant reorganizations. These
network organizations are unlikley to be a project of environmental
forces because the changing points in non-assembling communities are
both less frequent and in different time points. The reorganizations
are thus a product of the assembly process.

There were no consistent trends as to when change points occurred
within assembling hedgerows or across all sites, except many site had
changing points between year 2009 and 2011 (Fig.~
\ref{fig:changePoints}). In California, 2011 marked the beginning of a
multi year drought. In the assembling hedgerows were not sampled in
2010, so disentangling whether the changing points are due to skipping
a year of assembly or the drought is not impossible. Interestingly,
most of the assembling hedgerows

The species that were most variable in their network position and thus
contributed most to network reorganizations where species with the
highest degrees (i.e., most generalized) and persistence.  For
example, the five most ubiquitous species in our study landscape ---
\textit{Halictus ligatus}, \textit{Halictus
  tripartitus},\textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- where also the only species that
changed what module (i.e., community) they were present in across
years in all of the assembling hedgerows. Because species degree and
persistence were strongly correlated, it is difficult to disentable
the causal mechanism for why species with their chatacterists are so
variable in their network position. Generalized species may be best
able to exploit the limited floral resources the intensivly managed
agriculture landscape, and thus also most persistent. These adaptable
species will take advanatge of the most advantage resrouces, which my
depend the other pollinator species that are present and the state of
the floral resource. More persistent species also have longer
phenologies, so they have the opportunity to visit many different
flowers, resulting in a high degree.  Either way, our results suggest
that highly persisitent and generalized species often change their
network positions.

Preferential attachment is the most widely accepted theory explaining
community assembly in mutualistic networks. Communities assembling
through preferential attachment are formed by a core of generalist
species, to which new species arriving to the community interact
with. Thus, communities assembling through preferential attachment
exhibit an increase both in nestedness and in the overall level of
species specialization, since specialist species are being added to
the community. However, our changing point analysis results show that
there is a critical reorganization in the interaction patterns as
communities assembly, which contradicts the preferential attachment
theory. Even though we encountered an increase in nestedness through
time, specialization did not increase. Furthermore, this increase in
nestedness could be explained by the increase in species
richness. blablabla mechanistic models.

%% not sure if we want to go here, since it is not really part of the
%% assembly story. More just a "hmm networks are structured in odd
%% ways sometimes"  
% Other interesting result is that even though nestedness increased
% through time, modularity and connectance did not. \cite{Fortuna2010}
% suggest that at low connectance levels, mutualistic networks would
% present high nestedness and high modularity, while at high connectance
% levels networks would present low nestedness and low
% modularity. However, our results show the contrary: early communities
% presented low nestedness, smaller richness, and higher levels of
% modularity and connectance, while more mature communities presented
% higher nestedness, higher richness, and smaller modularity and
% connectance. SO blabla... XX Temporal overlap.

% Evidence indicates that there is a positive relationship between
% abundance and diet breadth, with the more generalist species having
% higher abundances. Because of the high generalism, species more
% abundant also present higher degrees. Thus, we expected that more
% generalist species would be part of the network core. Surprisingly,
% the five most common species were also the ones that exhibited the
% most changes in interaction patterns. These species (names!) were
% always present in the periphery of the network. One hypotheses is that
% their high generalism allows them to explore the resources more
% broadly, allowing them to change their position in the network. XX
% mention the closeness variability and the species persistence.

High nestedness has been related to an increase in the robustness of
communities to species extinctions because the core of generalist
species would act as a buffer against species loss (REF). Similarly,
communities with greater modularity would be more robust in general,
because modules would act as a buffer against perturbation spreading
and the pervasive effects of species loss. We expected that as
communities assemble and species richness increase, communities would
become increasingly robust to species loss. however, we found that
robustness to species loss did not change through time. This is
interestingly from the conservation biology point of view, because
even early assembling communities seem to be as robust as more mature
communities, despite the richness insurance hypothesis. However,
communities are not only subjected to species loss, but also to other
types of perturbations that can cascade through the network. Gaiarsa
et al. (submitted) suggest using algebraic connectivity to explore
how vulnerable ecoogical communities might be to cascading
effects. Our results indicate that more mature communities are more
robust to cascading effects than early on assemblages, and that this
result is related to species richness. This migth be related to XX....

@@

We would like to thank Paulo Guimar{\~a}es Leto Peel and Aaron Clauset for
their invaluable discussions and for help with the change point
analysis.  We thank the growers and land owners that allowed us to
work on their property.  We also greatly appreciate the identification
assistance of expert taxonomists Martin Hauser, Robbin Thorp and Jason
Gibbs.  This work was supported by funding from the Army Research
Office (W911NF-11-1-0361 to CK), the Natural Resources Conservation
Service (CIG-69-3A75-12-253, CIG-69-3A75-9-142, CIG-68-9104-6-101 and
WLF-69-7482-6-277 to The Xerces Society), the National Science
Foundation (DEB-0919128 to CK), The U.S.  Department of Agriculture
(USDA-NIFA 2012-51181-20105 to Michigan State University).  Funding
for LCP was provided by an NSF Graduate Research Fellowship and the
USDA NIFA Graduate Fellowship. Funding for MPG was provided by S{\~a}o
Paulo Research Foundation (FAPESP, grant 2013/13319-5).
